---
title: "Developing Data Products Week 2 Assignment"
author: "Bill Lisse"
date: "May 15, 2023"

output: 
  html_document:
    keep_md: true
    theme: paper
    highlight: kate
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment="#/>")
```

## Introduction

The goal of this assignment is to create a web page using R Markdown that features a map created with Leaflet. The webpage should be hosted on either Github Pages, RPubs, or NeoCities. The webpage must also contain the date when the document was created.

## Top 50 Earthquakes

The map shows a sample of 50 ocean eartquakes based on magnitude near Sydney, Australia. code repository is located at  https://github.com/Spyguy3/Data_Products_Week2_Project.git

```{r}
# Load the required packages
library(leaflet)
set.seed(122)
# Sample the data for 50 observations
quakes1=quakes[sample(nrow(quakes),50),]

# create earthquake magnitude range to define the type as follows 
quakes1$magrange = cut(quakes1$mag, 
                      breaks = c(4, 5, 6, 7), right=FALSE,
                      labels = c("Light[4-5)", "Moderate[5-6)", "Strong[6-7)"))

# Define a color pallete corresponding to the magnitude ranges
pal = colorFactor(palette = c("yellow", "red", "black"), domain=quakes1$magrange)

# Create the map object & add circle marker
leaflet(data=quakes1) %>% 
  addProviderTiles("Esri.WorldImagery") %>% 
  addMarkers(lng=151.209900, lat=-33.865143, popup = "Sydney, Australia") %>% 
  addCircleMarkers(lng = ~ long, 
                   lat= ~ lat, 
                   color = ~ pal(magrange), #use the pallete
                   label = paste("Magnitude=", quakes1$mag, "Type=", quakes1$magrange)

                   )
```

